### 2014-12-02 Neutral_simulPow.Rmd
Finishing conclusion

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.001,0.01,0.1))
g

>>>>

# Plot of the spatial pattern for Neutral model with Logseries SAD with 8,64,256 species and side=512/256
#
g <- plotNeutral_SpatPat(64,256,500,"L",c(0.1,1))
g <- plotNeutral_SpatPat(64,256,500,"L",c(0,0.01,0.1,1))
g
